---
title: "presentation_new"
output:
  html_document: default
  pdf_document: default
---

# Data Description

### IDA(Initial Data Analysis)

```{r}
birthwt=MASS::birthwt
?birthwt
```

```{r}
#factorize categorical variables
library(tidyverse)
birthwt$race=factor(birthwt$race,labels=c("white","black","other"))
birthwt$smoke=factor(birthwt$smoke,labels=c("No","Yes"))
birthwt$ht=factor(birthwt$ht,labels=c("No","Yes"))
birthwt$ui=factor(birthwt$ui,labels=c("No","Yes"))
birthwt$low=factor(birthwt$low,labels=c("No","Yes"))

```

```{r}
#rename columns to make it readable
colnames(birthwt) <- c("birthwt.below.2500", "mother.age",
"mother.weight", "race",
"mother.smokes", "previous.prem.labor",
"hypertension", "uterine.irr",
"physician.visits", "birthwt.grams")

```

\# birthwt%>%

\# ggplot()+

\# aes(x=birthwt.below.2500,y=birthwt.grams,color=birthwt.below.2500,group=birthwt.below.2500)+

\# labs(x="Low Birth Weight",y="BirthWeight",color="")+

\# geom_boxplot()+

\# geom_hline(yintercept=2500,linetype="dashed", color = "red", size=0.5)+

\# scale_y\_continuous(limits=c(1000,5000),breaks=seq(1000,5000,by=500))+

\# theme_bw()

# Appropriate Model Selection+Assumption Checking

## pairplot

```{r}
#pairplot
GGally::ggpairs(birthwt)
```

## Full model

```{r}
#full model
##without low, because low is the outcome
lm_full<- lm (birthwt.grams ~ . - birthwt.below.2500, data=birthwt)
summary(lm_full)
equatiomatic::extract_eq(lm_full,use_coefs = T) #we should further remove insignificant factors
equatiomatic::extract_eq(lm_full)
```

## Reduced Model

```{r}
#reduced model
#variable selection using AIC
lm_reduced=step(lm_full,direction="both",test="F",trace=F)
summary(lm_reduced)

equatiomatic::extract_eq(lm_reduced,use_coefs = T,font_size="tiny")

```

```{r}
#assumption checking of reduced model
library(ggfortify)
autoplot(lm_full,which=1:2)
autoplot(lm_reduced,which=1:2)#QUESTION:should we check assumption before the linear model?
```

## Log Model

```{# {r}
# #log model
# birthwt_log=lm (log(birthwt.grams) ~ . - birthwt.below.2500, data=birthwt)
# summary(birthwt_lm)
# autoplot(birthwt_log,which=1:2)
```

```{r}
# #assumption checking of log model
# birthwt_log_step=step(birthwt_log,test="F")
# equatiomatic::extract_eq(birthwt_log_step,use_coefs = T) 
# #assumption checking of log model
# summary(birthwt_log_step)
# autoplot(birthwt_log_step,which=1:2)
```

# Result

```{r}
#hist(birthwt$birthwt.grams,breaks=20)
```

```{r}
library(caret)

cv_full=train(
  birthwt.grams ~ . - birthwt.below.2500,
  data=birthwt,
  method="lm",
  trControl=trainControl(
    method="cv",number=10,
    verboseIter=FALSE
    )
  )

cv_full

cv_reduced=train(
  lm_reduced$call$formula,
  data=birthwt,
  method="lm",
  trControl=trainControl(
    method="cv",number=10,
    verboseIter=FALSE
    )
  )

cv_reduced


# cv_reduced_log_linear=train(
#   birthwt_log_step$call$formula,
#   data=birthwt,
#   method="lm",
#   trControl=trainControl(
#     method="cv",number=10,
#     verboseIter=FALSE
#     )
#   )
# 
# cv_reduced_log_linear

df <- bind_rows(cv_full$results, cv_reduced$results)
df$model <- c("full", "reduced")
library(ggpubr)
p1 <- ggplot(df, aes(x=model, y=RMSE, group=1)) + geom_line() + geom_point()
p2 <- ggplot(df, aes(x=model, y=MAE , group=1)) + geom_line() + geom_point()

ggarrange(p1, p2, nrow = 1)
```

```{r}
sjPlot::tab_model(lm_full, lm_reduced,digits=4,show.ci=FALSE, show.aic=TRUE, dv.labels=c("Full Model","Reduced Model"),show.r2=TRUE)
?tab_model
```
